---
title: "Bootstarpping from normal and exponential distributions"
author: "MessaA"
date: "June 8, 2016"
output: html_document
---
 #**Bootstrapping from normal random distribution**  
   ##** a) Sample with size=50, mean=25, SD=6**
```{r Bootstarping1}
x<-rnorm(50,25,6)
M=mean(x)
Replicate<-1000
bootnorm1<-numeric(Replicate)
for(i in 1:Replicate){
temp<-sample(x,50,replace=T)
bootnorm1[i]<-mean(temp)
}
```
 ###**Summary of bootnorm1**  
```{r summary1}
summary(bootnorm1)

```  
 ###**Comparing means and standard deviations of orginal sample and bootstrapsamples**  
```{r Mean.SD1}
M
mean(bootnorm1)
sd(x)
sd(bootnorm1)


```  
 ###**Histogram of bootstarp samples and some comparisons such as means of orginal and bootstrap**  
```{r Histogram1}
hist(bootnorm1)
abline(v=M,col="blue", lwd=2, lty=2)
abline(v=mean(bootnorm1),col="red", lwd=2, lty=3)
abline(v=25,col="black", lwd=2, lty=4)

```    
  
 ###**Estimation of bias which can be caused due to random samples of randoms and source of variablity of bootstraping itself**
```{r Bias1}
est.bias1<-M-mean(bootnorm1)
est.bias1

```  
      
    
      ##** b) Sample with size=100, mean=25, SD=6**
```{r Bootstarping2}
x<-rnorm(100,25,6)
M2=mean(x)
Replicate<-1000
bootnorm2<-numeric(Replicate)
for(i in 1:Replicate){
temp<-sample(x,100,replace=T)
bootnorm2[i]<-mean(temp)
}
```
 ###**Summary of bootnorm2**  
```{r summary2}
summary(bootnorm2)

```  
 ###**Comparing means and standard deviations of orginal sample and bootstrapsamples**  
```{r Mean.SD2}
M2
mean(bootnorm2)
sd(x)
sd(bootnorm2)

```  
 ###**Histogram of bootstarp samples and some comparisons such as means of orginal and bootstrap**  
```{r Histogram2}
hist(bootnorm2)
abline(v=M2,col="blue", lwd=2, lty=2)
abline(v=mean(bootnorm2),col="red", lwd=2, lty=3)
abline(v=25,col="black", lwd=2, lty=4)

```    
  
 ###**Estimation of bias which can be caused due to random samples of randoms and source of variablity of bootstraping itself**
```{r Bias2}
est.bias2<-M2-mean(bootnorm2)
est.bias2
```

  #**Bootstrapping from exponential random distribution**  
   ##**a) Sample with size=75, lambda(rate)=0.2, where mean=sd=1/lambda**
```{r Bootstarping3}
x<-rexp(75,0.2)
M3=mean(x)
Replicate<-1000
bootexp3<-numeric(Replicate)
for(i in 1:Replicate){
temp<-sample(x,75,replace=T)
bootexp3[i]<-mean(temp)
}
```
 ###**Summary of bootexp3**  
```{r summary3}
summary(bootexp3)

```  
 ###**Comparing means and standard deviations of orginal sample and bootstrapsamples**  
```{r Mean.SD3}
M3
mean(bootexp3)
sd(x)
sd(bootexp3)
```  
 ###**Histogram of bootstarp samples and some comparisons such as means of orginal and bootstrap**  
```{r Histogram3}
hist(bootexp3)
abline(v=M3,col="blue", lwd=2, lty=2)
abline(v=mean(bootexp3),col="red", lwd=2, lty=3)
abline(v=5,col="black", lwd=2, lty=4)

```    
  
 ###**Estimation of bias which can be caused due to random samples of randoms and source of variablity of bootstraping itself**
```{r Bias3}
est.bias3<-M3-mean(bootexp3)
est.bias3

```  
      
    
       ##** b)Sample with size=200, lambda(rate)=0.2, where mean=sd=1/lambda**
```{r Bootstarping4}
x<-rexp(200,0.2)
M4=mean(x)
Replicate<-1000
bootexp4<-numeric(Replicate)
for(i in 1:Replicate){
temp<-sample(x,200,replace=T)
bootexp4[i]<-mean(temp)
}
```
 ###**Summary of bootexp4**  
```{r summary4}
summary(bootexp4)

```  
 ###**Comparing means and standard deviations of orginal sample and bootstrapsamples**  
```{r Mean.SD4}
M4
mean(bootexp4)
sd(x)
sd(bootexp4)

```  
 ###**Histogram of bootstarp samples and some comparisons such as means of orginal and bootstrap**  
```{r Histogram4}
hist(bootexp4)
abline(v=M4,col="blue", lwd=2, lty=2)
abline(v=mean(bootexp4),col="red", lwd=2, lty=3)
abline(v=5,col="black", lwd=2, lty=4)

```    
  
 ###**Estimation of bias which can be caused due to random samples of randoms and source of variablity of bootstraping itself**
```{r Bias4}
est.bias4<-M4-mean(bootexp4)
est.bias4
```







